\documentclass{article}
\usepackage[utf8]{inputenc}    % For UTF-8 character encoding
\usepackage[T1]{fontenc}       % For proper font encoding
\usepackage{lmodern}           % Improved font rendering
\usepackage{amsmath}   % For advanced mathematical formatting
\usepackage{amssymb}   % For mathematical symbols
\usepackage{geometry}  % Adjust page margins
\usepackage{enumerate} % For custom lists
\usepackage{xcolor}  % for coloring
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\usepackage{listings}  % for code listings

\lstset{frame=tb,
  language=C,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,   
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{brown},
  stringstyle=\color{orange},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\geometry{top=1in, bottom=1in, left=1in, right=1in}

\begin{document}

\title{Longest Cycle in a Graph}
\author{Wang Xiyu}
\date{23 Dec 2024}
\maketitle

\section*{Problem Statement}
Given a directed weighted graph, find the length of the longest cyclic path. 
\section*{Problem Constraints}
\subsection*{Easy}
0..1 outgoing edge per node.
\subsection*{Generalized}
0..* outgoing edges per node.
\subsection*{Variation}
The graph is acyclic, find the longest path (critical path). All edges have non-negative weights.
\section*{Concept Proof}
\subsection*{Easy}
Since $\forall v \in V, |E_v: \{e | e \in E \land e(v, v')\}| <= 1$, $\nexists e \in E, e$ 
belongs to more than one possible cycle, and $\nexists v \in V, v$ belongs to more than one possible cycle.
$\implies$ if we have visited a $v \in G$, 

\begin{theorem}
    If there exist more than one cycle in a graph of said constraints, they are in disconnected components.
\end{theorem}
\begin{proof}
    \indent From the definition of cycle, and problem constriants,
    \[\forall v \in C, (v, v') \in E \implies v' \in C\]
    Which implies a cycle would not have an outgoing edge. Group all $v \in C$ to $v'', v'' $ has no outgoing edge $\implies v'' $ is a sink.
    Suppose there are more than one cycle in a connected component in 
    $G, $
    \[\exists v\in V, \forall v_{C1} \in C_1, \forall v_{C2} \in C_2, v \vdash^* v_{C1} \land v \vdash^* v_{C2}\]
    $\implies \exists v_{branch}(v \vdash^* v_{branch} \land v_{branch} \vdash v_{C1} \land v_{branch} \vdash v_{C2})$ has more than one outgoing edge, a contradiction.
\end{proof}
\noindent Therefore, it is possible to enumerate all cycles in $G$ in one iteration of the edge array, and the longest among which is the solution.
\subsection*{Generalized}
The generalized version of this problem is NP-Complete, as it can be reduced from Hamitonian Circuit. Scenario-specific techniques need to be employed
to derive an efficient algorithm. 

\begin{theorem}
    Longest cycle in a directed weighted graph is NP-Complete.
\end{theorem}
\begin{proof} 
    Longest cycle is NP. \newline
    \newline
    Consider the decision version of the problem: if $\exists $ a cycle in graph $G$ that has total lenght $\geq k$.
    It is trivial to show that both checking if a set of vertices forms a cycle, and summing up the lenght of involved edges takes polynomial time. 
    \newline
    Longest cycle is NP-hard.\newline
    \newline
    Equivalent to Longest path in directed graph, by starting and ending in the same vertex.
\end{proof}
\subsection*{Variation: Longest path in DAG}
use topological sort and DP 
\section*{Solution}
\subsection*{Easy}
\begin{lstlisting}
class Solution {
    public:
        int maxLength = -1;
        void getcycle(vector<int> &edges,int start,
                    vector<bool>& visit,vector<int>& store){
            if(start == -1)return ; // if prev node leads to nowhere, current node is a sink
            if(visit[start]){ // if the node is already visited
                int count = -1; 
                for(int i =0;i<store.size();i++){
                    if(store[i]==start){ // if current node has been recorded
                        count = i; // set count to be the index of start in store
                        break;
                    }
                }
                if(count==-1)return; // if current node is not found in a path 
                                     // -> no cycle in current component
                int size = (store.size()-count); 
                maxLength = max(maxLength,size); // update current max cycle length
                return ;
            }
            visit[start] = true; // mark this node as visited
            store.push_back(start); // mark this node as appeared in current path
            getcycle(edges,edges[start],visit,store); // edges[start] -> start.next
            return ; // finish exploring a component
        }
        int longestCycle(vector<int>& edges) { 
            vector<bool> visit(edges.size(),0);
            for(int i =0;i<edges.size();i++){
                if(visit[i])continue; // node i is in an already explored component
                vector<int> store;
                getcycle(edges,i,visit,store); // find the cycle length 
                                               // (if existent) in the component containing i
            }
            return maxLength;
        }
    };
\end{lstlisting}

\subsection*{Variation: Longest path in DAG}
\begin{lstlisting}
    class Solution {
        public:
            vector<int> dist;
            vector<bool> visited;
            void dfs(vector)
    };
\end{lstlisting}
\end{document}
