\documentclass{article}
\usepackage[utf8]{inputenc}    % For UTF-8 character encoding
\usepackage[T1]{fontenc}       % For proper font encoding
\usepackage{lmodern}           % Improved font rendering
\usepackage{amsmath}   % For advanced mathematical formatting
\usepackage{amssymb}   % For mathematical symbols
\usepackage{geometry}  % Adjust page margins
\usepackage{enumerate} % For custom lists
\usepackage{xcolor}  % for coloring
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\usepackage{listings}  % for code listings

\lstset{frame=tb,
  language=C,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,   
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{brown},
  stringstyle=\color{orange},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\geometry{top=1in, bottom=1in, left=1in, right=1in}

\begin{document}

\title{Poor pigs}
\author{Wang Xiyu}
\date{26 Dec 2024}
\maketitle

\section*{Problem Statement}
Given integer $n, t_1, t_2$, number of buckets, among which exactly one bucket contains poison; 
time taken for poison to kill a pig, and total time allowed. Find the minimum number of pigs needed to
find the bucket containing poison within total time allowed.
\section*{Problem Constraints}
\section*{Concept Proof}
\begin{theorem}
    $p$ pigs and $q$ attempts can find the poisonous bucket among $(q+1)^p$ buckets.
\end{theorem}
\begin{proof}
    Proof by Induction: 
    \subsection*{Induction over attempts} 
    Base case: One attempt allowed $\implies 2^p$ buckets to be searched. Encode each bucket in binary,
    where at digit $i$ a 0 represents it not being consumed by pig $i$, 1 otherwise. It is clear that for every possible 
    poisonous bucket, there exists a unique pattern of dead pigs, thus sufficient to identify the bucket. 
    \newline
    Inductive step: Suppose with $q$ attempts, $(q+1)^p$ buckets can be searched. 
\end{proof}
\begin{corollary}
    To find the poisonous bucket among $n$ buckets, in $x$ attempts, $\lceil log_x(n) \rceil$ pigs are needed.
\end{corollary}
\section*{Solution}
\subsection*{Easy}

\end{document}
